---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# simulreturns

<!-- badges: start -->
<!-- badges: end -->

The goal of simulreturns is to give access to user-friendly tools for computing the final value of an investment project.

## Installation

You can install the development version of simulreturns from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Layalchristine24/simulreturns")
```

## Example

This is a basic example which shows you how to solve compute the final value of an investment of 5000 units after 30 periods, with compound interests and immediate annuities, assuming an expected return of 10\% in average and annuities of 12000 units.

```{r example}
library(simulreturns)
library(ggplot2)
library(dplyr)

.n_per <- 30
.v_0 <- 5000
.exp_return <- 10
.compound <- TRUE
.x_yearly <- 12000
.immediate <- TRUE
# Compound return, with immediate annuities
FINAL_VALUE_CMP_IMM_ANNUITIES <- get_final_value(
  n_per = .n_per,
  v_0 = .v_0,
  exp_return = .exp_return,
  compound = .compound,
  x_yearly = .x_yearly,
  immediate = .immediate
)
```



```{r summary_final_value}
summary(FINAL_VALUE_CMP_IMM_ANNUITIES)
```



```{r plot_final_value, echo = FALSE}
FINAL_VALUE_CMP_IMM_ANNUITIES %>% 
  ggplot(aes(x = period, y = final_value)) +
  geom_line(size = 1.1) +
  theme_light() +
  labs(
    title = "Final value of an investment, with compound interests and immediate annuities",
    subtitle = paste0("Number of periods: ",.n_per, " initial capital: ", .v_0, "exp. return: ", .exp_return, " annuities: ", .x_yearly),
    x = "Periods",
    y = "Final value after x periods",
    caption = paste(
      format(Sys.Date(), "%d.%m.%Y"),
      "Layal Lettry",
      sep = ", "
    )
  ) +
  theme(
    legend.position = "bottom", axis.text = element_text(size = 12),
    axis.title = element_text(size = 12)
  ) 
# +
#   scale_x_discrete(breaks = c(20, 30, 40, 50, 60, 70, 80, 90)) +
#   scale_color_discrete("Sexe", labels = "Femme", "Homme")
  
```

